Ethereum: A Secure Decentralised Generalised Transaction Ledger \\ {\smaller \textbf{Byzantium version \YellowPaperVersionNumber}}

### 2018-02-21 Paper.tex

The normal halting function $H$ is defined:
\begin{equation}
H(\boldsymbol{\mu}, I) \equiv \begin{cases}
H_{\text{\tiny RETURN}}(\boldsymbol{\mu}) & \text{if} \quad w \in \{\text{\small \hyperlink{RETURN}{RETURN}}, \text{\small REVERT}\} \\
() & \text{if} \quad w \in \{ \text{\small STOP}, \text{\small \hyperlink{selfdestruct}{SELFDESTRUCT}} \} \\
\varnothing & \text{otherwise}
\end{cases}
\end{equation}

@@

We define $\Xi_{\mathtt{ERCEC}}$ as a precompiled contract for the elliptic curve digital signature algorithm (ECDSA) public key recovery function (ecrecover). See Appendix \ref{app:signing} for the definition of the function $\mathtt{\tiny ECDSARECOVER}$. We also define $\mathbf{d}$ to be the input data, well-defined for an infinite length by appending zeroes as required. In the case of an invalid signature ($\mathtt{\tiny ECDSARECOVER}(h, v, r, s) = \varnothing$), we return no output.

>>>>

The normal halting function $H$ is defined:
\begin{equation}
H(\boldsymbol{\mu}, I) \equiv \begin{cases}
H_{\text{\tiny RETURN}}(\boldsymbol{\mu}) & \text{if} \quad w \in \{\text{\small \hyperlink{RETURN}{RETURN}}, \text{\small REVERT}\} \\
() & \text{if} \quad w \in \{ \text{\small \hyperlink{stop}{STOP}}, \text{\small \hyperlink{selfdestruct}{SELFDESTRUCT}}\} \\
\varnothing & \text{otherwise}
\end{cases}
\end{equation}

@@

We define $\Xi_{\mathtt{ERCEC}}$ as a precompiled contract for the elliptic curve digital signature algorithm (ECDSA) public key recovery function (ecrecover). See \ref{app:signing} for the definition of the function $\mathtt{\tiny ECDSARECOVER}$. We also define $\mathbf{d}$ to be the input data, well-defined for an infinite length by appending zeroes as required. In the case of an invalid signature ($\mathtt{\tiny ECDSARECOVER}(h, v, r, s) = \varnothing$), we return no output.
